---
title: "ADS 503 Project"
author: "Eva Chow"
date: '2022-06-08'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Libraries
## REMOVE NOTE LATER - ggplot and dplyr are part of tidyverse, so removed them. 
```{r message=FALSE, warning=FALSE}
library(haven)
library(caret)
library(gridExtra)
library(corrplot)
library(e1071)
library(car)
library(lattice)
library(doParallel)
library(RANN)

library(tidyverse)
```

# Set up Parallelization - Note, you can reduce number of clusters if needed not sure if R does it automatically if you set over the number of cores on your CPU
```{r}
cl <- makeCluster(6)
registerDoParallel(cl)
```


# Read in data
```{r}
Demographic <- read_xpt("P_DEMO.XPT")
BodySize <- read_xpt("P_BMX.XPT")
Chol_ldl <- read_xpt("P_TRIGLY.XPT")
```

# Create Dataset
Chol-ldl
```{r}
#Select Variables of interest
Chol_ldl <- Chol_ldl %>% select(SEQN, LBDLDL)
#NA in target feature won't be useful
Chol_ldl <- Chol_ldl %>% drop_na()
```

Demographic
```{r}
#Get rid of variables we don't need
Drop_col <- c('SDDSRVYR', 'RIDSTATR', 'RIDEXMON', 'SIAPROXY', 'SIAINTRP', 'FIAPROXY', 'FIAINTRP', 'MIAPROXY', 'MIAINTRP', 'WTINTPRP', 'WTMECPRP', 'SDMVPSU', 'SDMVSTRA')
Demographic <- Demographic %>% select(-one_of(Drop_col))
```

BodySize
```{r}
Drop_col <- c('BMIWT', 'BMIRECUM', 'BMIHEAD', 'BMIHT', 'BMILEG', 'BMIARML', 'BMIARMC', 'BMIWAIST', 'BMIHIP', 'BMDSTATS')
BodySize <- BodySize %>% select(-one_of(Drop_col))
```

Join
```{r}
J1 <- Chol_ldl %>% left_join(Demographic, by = "SEQN")
Chol <- J1 %>% left_join(BodySize, by = "SEQN")
Chol <- Chol %>% select(!SEQN)
```

# Cleaning
## Changing factors for EDA 
## Changing Variables to the Correct Type 
```{r}
Chol_2 <- Chol
factors <- c("RIAGENDR", "RIDRETH1", "RIDRETH3", "DMDBORN4", "DMDEDUC2", "DMDMARTZ", "RIDEXPRG", "SIALANG", "FIALANG", "MIALANG", "AIALANGA")
Chol_2[,factors] <- lapply(Chol_2[,factors], factor)
```

## Change factor levels to be more interpretable
```{r}
levels(Chol_2$RIAGENDR) <- c("Male", "Female")
levels(Chol_2$RIDRETH1) <- c("Mex", "OHis", "White", "Black", "Oth")
levels(Chol_2$RIDRETH3) <- c("Mex", "OHis", "White", "Black", "Asian", "Oth")
levels(Chol_2$DMDBORN4) <- c("USA", "Oth", "Ref", "DK")
levels(Chol_2$DMDYRUSZ) <- c("<5", "5-15", "15-30", ">30", "Ref", "DK")
levels(Chol_2$DMDEDUC2) <- c("<9", "9-11", "HS", "AA", "BS+", "Ref", "DK")
levels(Chol_2$DMDMARTZ) <- c("Mar", "Sep", "Nev", "Ref", "DK")
levels(Chol_2$RIDEXPRG) <- c("Yes", "No", "DK")
levels(Chol_2$SIALANG) <- c("English", "Spanish")
levels(Chol_2$FIALANG) <- c("English", "Spanish")
levels(Chol_2$MIALANG) <- c("English", "Spanish")
levels(Chol_2$AIALANGA) <- c("English", "Spanish", "Asian")
```


# EDA
## NAs
### By Variable - Removed variables with over 3000 observations missing
```{r message=FALSE, warning=FALSE}
Variable_na <- Chol_2 %>% select(everything()) %>% summarise_all(funs(sum(is.na(.)))) %>% pivot_longer(cols = c(colnames(Chol_2[,1:ncol(Chol_2)])), names_to = "Variable", values_to = "Missing") %>% arrange(desc(Missing))
Drop_col <- c("RIDAGEMN", "BMXRECUM", "BMXHEAD", "BMDBMIC", "RIDEXPRG", "DMDYRUSZ")
Chol_2 <- Chol_2 %>% select(-one_of(Drop_col))
```

### By Row
```{r}
row_na <- rowSums(is.na(Chol_2))
row_na <- data.frame(row_na, Row = c(1:length(row_na)))
row_na <- row_na %>% arrange(desc(row_na))
#Most missing values in a row is 12, not bad
```

## Distributions
### Response - LDL Cholesterol
```{r}
#Looks like a fairly normal distribution, maybe a little skewed to the right. 
ggplot(Chol_2, aes(x = LBDLDL)) + geom_histogram() + ggtitle("LDL Distribution Histogram")
skewness(Chol_2$LBDLDL)
#skewness value .7886403 confirms very mild skewness to the right
```

### Predictors
Factors
```{r}
Chol_fact <- Chol_2 %>% select_if(is.factor)
Chol.bar <- function(xvar){
  ggplot(Chol_fact, aes_(x = as.name(xvar))) +
    geom_bar(color = "black") + coord_flip()
}
Lang_barplots <- lapply(names(Chol_fact[,7:10]), Chol.bar)
Oth_barplots <- lapply(names(Chol_fact[,1:6]), Chol.bar)
grid.arrange(grobs = Lang_barplots, top = "Language Features")
grid.arrange(grobs = Oth_barplots, top = "Other Demographics")
```

Numeric
```{r message=FALSE, warning=FALSE}
Chol_num <- Chol_2 %>% select_if(is.numeric) %>% select(!LBDLDL)
Chol.hist <- function(xvar){
  ggplot(Chol_num, aes_(x = as.name(xvar))) +
    geom_histogram(color = "black") 
}
Dem_hist <- lapply(names(Chol_num[,1:2]), Chol.hist)
Body_hist <- lapply(names(Chol_num[,3:10]), Chol.hist)
grid.arrange(grobs = Dem_hist, top = "Demographic Features")
grid.arrange(grobs = Body_hist, top = "Body Measures")
```

## Correlations
Heatmap
```{r}
Chol_dummy <- fastDummies::dummy_cols(Chol_2)
Chol_dummy <- Chol_dummy %>% select_if(~!is.factor(.))
Chol_dummy[] <- lapply(Chol_dummy, as.numeric)
Chol_cor <- cor(Chol_dummy, use = "complete.obs")
Chol_corplot <- corrplot(cor(Chol_dummy, use = "complete.obs"), tl.pos = 'n')
#Looks like some dummy variables that are refusal could be messing up correlations
Drop_col <- c("DMDBORN4_Ref", "DMDBORN4_DK", "DMDEDUC2_Ref", "DMDEDUC2_DK", "DMDEDUC2_NA", "DMDMARTZ_Ref", "DMDMARTZ_NA", "FIALANG_NA", "MIALANG_NA", "AIALANGA_NA")
Chol_dummy_2 <- Chol_dummy %>% select(-one_of(Drop_col))
cor(Chol_dummy_2, use = "complete.obs")
corrplot(cor(Chol_dummy_2, use = "complete.obs"), tl.pos = 'n', type = 'lower')
```
```{r}
# Mini Correlations: Sociological Measures:
socio <- Chol_dummy_2[,c("RIAGENDR_Male","RIAGENDR_Female",
                       "RIDRETH1_Mex", "RIDRETH1_OHis", "RIDRETH1_White", 
                       "RIDRETH1_Black", "RIDRETH1_Oth", "RIDRETH3_Mex", "RIDRETH3_OHis",
                       "RIDRETH3_White", "RIDRETH3_Black", "RIDRETH3_Asian", "RIDRETH3_Oth",
                       "DMDBORN4_USA", "DMDBORN4_Oth", "DMDEDUC2_<9", "DMDEDUC2_9-11",
                       "DMDEDUC2_HS", "DMDEDUC2_AA", "DMDEDUC2_BS+","DMDMARTZ_Mar",
                       "DMDMARTZ_Sep", "DMDMARTZ_Nev", "DMDMARTZ_DK", "SIALANG_English", 
                       "SIALANG_Spanish", "FIALANG_English", "FIALANG_Spanish",
                       "MIALANG_English","MIALANG_Spanish", "AIALANGA_English",
                       "AIALANGA_Spanish", "AIALANGA_Asian", "LBDLDL")]

cor(socio, use = "complete.obs")
corrplot(cor(socio, use = "complete.obs"), tl.pos = 'y', type = 'lower', 
         order = "hclust", tl.cex = 0.5)
```
```{r}
# Mini Correlations: Biological Measures:
biologic <- Chol_dummy_2[,c("RIDAGEYR", "BMXWT", "BMXHT", "BMXBMI", 
                            "BMXLEG", "BMXARML", "BMXARMC", "BMXWAIST",
                            "BMXHIP", "RIAGENDR_Male", "RIAGENDR_Female","LBDLDL")]
cor(biologic, use = "complete.obs")
corrplot(cor(biologic, use = "complete.obs"), tl.pos = 'y', type = 'lower', 
         order = "hclust", tl.cex = 0.8)
# correlations between certain biological measures make sense. BMI is derived from the MASS and height of an individual, so it makes sense that many of the BMI measurements correlate with each other. (i.e. hip, waist, and weight measurements correlate with a higher BMI. Being female correlates negatively with leg and arm length as well as height)
```

# REMOVE NOTE LATER - MAY NEED TO USE DUMMY CHOL DATA FOR HIGH CORRELATIONS - REGULAR CHOL STILL HAS CATEGORICAL VARIABLES AS SINGLE NUMERIC VARIABLES.
```{r}
# let's check for highly correlated predictors
# we'll do this on our non factor transformed dataset
dim(Chol)

# 27 variables. let's find correlations greater than 0.80 and see how the data looks if removed
corr_Chol <- cor(Chol)

# if removed, how many variables are left
high_corr_Chol <- findCorrelation(corr_Chol, cutoff = 0.80)
no_corr_Chol <- Chol[, -high_corr_Chol]
dim(no_corr_Chol)
```
# Checking things above with Dummy Variable Data
## CURRENTLY TESTING STUFF HERE FOR HOW TO DEAL WITH DUMMY DATA WITH COR
```{r}
testdata <- Chol_dummy
testdata <- apply(Chol_dummy, 2, function(y) {y[!is.finite(y)] = NA; y})
testdata <- testdata[complete.cases(testdata), ]
testdata <- testdata[, -nearZeroVar(testdata)]
testdata <- data.frame(testdata)
dim(Chol_dummy)
Cor_chol_dummy <- cor(testdata)
high_corr_dummy <- findCorrelation(Cor_chol_dummy, cutoff = 0.8)
```

```{r}
# looking at a base linear model, to see significant variables 
model0 <- lm(LBDLDL~., Chol_2)
summary(model0)
  # significant contributors: variable (Pr(>|t|)) 
    # RIDAGEYR (0.000132)
    # (Intercept) (0.043474)
    # MDBORN4Oth (0.076414) 
    # AIALANGASpanish (0.041803)
    # BMXLEG (0.033051)
    # BMXARMC (0.004507) 
    # BMXWAIST (0.071888)
```

```{r}
# looking at VIF for baseline linear:
vif(model0)
  # highly/perfectly correlated factors, we might need to drop some
```

# Degenerate Predictors
```{r}
# Let's check for degenerate predictors from the original dataset
nearZeroVar(Chol, saveMetrics = FALSE)
deg_chol <- subset(Chol, select=c(4,11,16,18,19))
colnames(deg_chol)

# Do it again on factor dataset
nearZeroVar(Chol_2, saveMetrics = FALSE)
deg_chol2 <- subset(Chol_2, select=c(13))
colnames(deg_chol2)

# we may have to consider removing depending on the data used for modeling
```



# Splitting
#NOTE SWITCHED TRAINING TO DUMMY
```{r}
# set the seed and split the data. We'll do an 80/20 split
set.seed(123)
Chol_split <- createDataPartition(Chol$LBDLDL, p=0.80, list=FALSE)

# split into train and test
Chol_train <- Chol_dummy[Chol_split,]
Chol_test <- Chol_dummy[-Chol_split,]

# split predictors from the target
Chol_train_X <- as.data.frame(subset(Chol_train, select=-c(LBDLDL))) 
Chol_train_y <- Chol_train$LBDLDL

Chol_test_X <- as.data.frame(subset(Chol_test, select=-c(LBDLDL)))
Chol_test_y <- Chol_test$LBDLDL

# Creating imputed data sets
Chol_imp <- preProcess(Chol_train_X, method = c("center", "scale", "knnImpute"))
Chol_train_X_imp <- predict(Chol_imp, Chol_train_X)
Chol_test_X_imp <- predict(Chol_imp, Chol_test_X)

# Adding Resampling/Validation Set and Control 
set.seed(123)
Chol_folds <- createFolds(y = Chol_train_X, k = 10, returnTrain = T)
Chol_control <- trainControl(method = "cv", index = Chol_folds)
```


# Linear Models - Hunter
## OLS 
### Create Initial Model
```{r}
Chol_ols_tune <- train(x = Chol_train_X_imp, y = Chol_train_y, method = "lm", trControl = Chol_control)
plot(Chol_ols_tune$finalModel)
```
### FIX TRAINING SET
```{r}
# VIF shows aliased coefficients, need to get rid of those by removing high cor predictors
test <- cor(Chol_train_X_imp)
# Also have an issue with DMDEDUC2_DK all being zero so get rid of high var predictors
Chol_tr_x_imp_vr <- Chol_train_X_imp[, -nearZeroVar(Chol_train_X_imp)]
Chol_tr_X_imp_fin <- Chol_tr_x_imp_vr[, -findCorrelation(cor(Chol_tr_x_imp_vr), cutoff = 0.9)] 
```

### Tune Another Model
```{r}
Chol_ols_tune2 <- train(x = Chol_tr_X_imp_fin, y = Chol_train_y, method = "lm", trControl = Chol_control)
plot(Chol_ols_tune2$finalModel)
summary(Chol_ols_tune2$finalModel)
```

### Final OLS Model
```{r}
Chol_sig_tr <- Chol_tr_X_imp_fin %>% select(RIDAGEYR, BMXHT, BMXBMI, BMXLEG, BMXARMC,  DMDBORN4_Oth, DMDEDUC2_NA, MIALANG_NA, AIALANGA_NA)
Chol_ols <- train(x = Chol_sig_tr, y = Chol_train_y, method = "lm", trControl = Chol_control)
plot(Chol_ols$finalModel)
summary(Chol_ols$finalModel)

#Predict on test data
Chol_ols_res <- predict(Chol_ols, Chol_test_X)
```


